---
title: Details on demand
description: UI that's out of sight but within reach
duration: 25min
---

[bsicons]: https://cran.r-project.org/package=bsicons
[fontawesome]: https://rstudio.github.io/fontawesome/

```{r}
#| include: false
library(shiny)
library(bslib)
```

## Outline

* [Popovers](#popovers) and [Tooltips](#tooltips) (10)
* [Your turn: breakout exercise](#your-turn) (5)
* [Accordions](#accordions) (10)

## Popovers

Popovers are like small modals that appear when you click on an element, like an icon.
Because they're persistent, they're great for a bit of extra information or a small number of additional controls, like plot settings.

Popovers pair well with buttons or icons, like those from [bsicons] or [fontawesome].
Just be certain to use recent versions of either package and to include a `title` attribute for accessibility.

```{r}
popover(
  bsicons::bs_icon("gear", title = "Settings"),
  "... content that appears in the popover",
)

popover(
  shiny::actionButton("settings", "Settings"),
  "... content that appears in the popover",
)
```

The `card_header()` or `card_footer()` is a great place to put popovers, and you can use Bootstrap's [hstack feature](https://getbootstrap.com/docs/5.3/helpers/stacks/#horizontal) and [flex utility classes](https://getbootstrap.com/docs/5.3/utilities/flex/#justify-content) to help position the trigger element.

```{r}
card(
  card_header(
    class = "hstack justify-content-between",
    "Cost vs. Earnings",
    popover(
        bsicons::bs_icon("gear", title = "Settings"),
        "Choose the grouping variable"
    )
  ),
  "Imagine a plot here."
)
```

## Tooltips

Tooltips are ephemeral bits of additional context.
They work well when paired with an icon in the label of an input.

```{r}
textInput(
  inputId = "school_search",
  label = tagList(
    "Search for School",
    tooltip(
      bsicons::bs_icon("info-circle", title = "About search"),
      "Regular expressions are not supported, sorry."
    )
  )
)
```

`card_header()` and `card_footer()` are also great places to place tooltips.
Again the `.hstack` Bootstrap class is helpful for organizing a row of icons.

```{r}
card(
  card_header(
    class = "hstack justify-content-between",
    "Cost vs. Earnings",
    div(
      class = "hstack gap-2",
      popover(
          bsicons::bs_icon("gear", title = "Settings"),
          "Choose the grouping variable"
      ),
      tooltip(
        bsicons::bs_icon("info-circle", title = "Info"),
        "You should probably know this by now, but..."
      )
    )
  ),
  "Imagine a plot here."
)
```

## 🧑‍💻 Your Turn

::: lead
<i class="bi bi-folder-symlink-fill"></i> `exercises/07_app.R`
:::

Looking back at our use of a navset card in the last exercise, we might be able to improve the design and user experience with a popover.

In `exercises/07_app.R`, I've reset the app to use a single plot output with a radio button input.
Use a `popover()` to hide the radio buttons in a menu in the card header.

💡 Looking for icon inspiration? Check out [Bootstrap icons](https://icons.getbootstrap.com/).

## Accordions

- popover
    - lead in from navset card --> popover
- tool tip
- accordion